Signatures and Induction Principles for Higher Inductive-Inductive Types

### 2019-08-14 paper.tex
infinitary lambda comment

We do not include a $\lambda$ in the syntax. The reason is twofold; first,

@@

(7) $\U$ is also closed under a function space where the domain is an external
type and the codomain is a small source theory type. We overload the application
notation for external parameters, as it is usually clear from context which
application is meant. The rules allow types with infinitary constructors, for
example trees containing elements of $\hat{A}$ at the leaves and branching by
$\hat{B}$ (which could be an infinite type):
\[
\hat{A}\in\Type_{\hat{0}}\commah\hat{B}\in\Type_{\hat{0}}\vdash\,\boldsymbol{\cdot},\,\,\,T:\U,\,\,\,leaf:(\hat{x}\in \hat{A})\ra\underline{T},\,\,\,node:((\hat{x}\in \hat{B})\ra T)\ra\underline{T}
\]
Here, $leaf$ has a function type (6) and $node$ has a function type (3) with a
function type (7) in the domain. More generally, we can define $W$-types
\cite{abbot05containers} as follows. $\hat{S}$ describes the ``shapes'' of the
constructors and $\hat{P}$ the ``positions'' where recursive arguments can
appear.
\[
\hat{S}\in\Type_{\hat{0}}\commah\hat{P}:\hat{S}\rah\Type_{\hat{0}}\vdash\,\boldsymbol{\cdot},\,\,\,W:\U,\,\,\,sup: (\hat{s} \in \hat{S})\ra((\hat{p} \in \hat{P}\,\hat{s})\ra W)\ra \underline{W}
\]
For a more complex infinitary example, see the definition of Cauchy
reals in \cite[Definition 11.3.2]{HoTTbook}. It can be also found as
an example file in our Haskell implementation.

>>>>

@@

(7) $\U$ is also closed under a function space where the domain is an
external type and the codomain is a small source theory type. We
overload the application notation for external parameters, as it is
usually clear from context which application is meant. The rules allow
types with infinitary constructors, for example, trees branching by a
possibly infinite external type $\hat{A}$:
\[
\hat{A}\in\Type_{\hat{0}}\vdash\,\boldsymbol{\cdot},\,\,\,T:\U,\,\,\,leaf:\underline{T},\,\,\,node:((\hat{x}\in \hat{A})\ra T)\ra\underline{T}
\]
Here, $node$ has a function type (3) with a function type (7) in the
domain. More generally, we can define $W$-types
\cite{abbot05containers} as follows. $\hat{S}$ describes the
``shapes'' of the constructors and $\hat{P}$ the ``positions'' where
recursive arguments can appear.
\[
\hat{S}\in\Type_{\hat{0}}\commah\hat{P}:\hat{S}\rah\Type_{\hat{0}}\vdash\,\boldsymbol{\cdot},\,\,\,W:\U,\,\,\,sup: (\hat{s} \in \hat{S})\ra((\hat{p} \in \hat{P}\,\hat{s})\ra W)\ra \underline{W}
\]
For a more complex infinitary example, see the definition of Cauchy
reals in \cite[Definition 11.3.2]{HoTTbook}. It can be also found as
an example file in our Haskell implementation.

Note that we do not include a $\lambda$ for infinitary function types,
although we could possibly use it when describing paths between such
functions. The reason is that $\lambda$ can be always represented in
signatures by introducing additional function parameters which are
constrained by pointwise equalities. For example, consider adding the
following path constructor to the previously described
$\hat{A}$-branching trees:
\[
eq : \underline{node\,(\lambda\,\hat{x}.\,leaf) =_T leaf}
\]
This can be rewritten without $\lambda$ as follows:
\[
eq : (f : \hat{A}\ra T)\ra ((\hat{x : A})\ra f \hat{x} =_T leaf)\ra\underline{node\,f =_T leaf}
\]
The benefit of supporting $\lambda$ would be less encoding noise in signatures. However,
we observe that such usage of $\lambda$ is rather rare in HITs in practice, and hence omit
$\lambda$ for the sake of simplicity.
